Conditional selectivity for triplestores

### 2012-09-18 conditional/trunk/selectivity-basic.tex
change todo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@380 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also have in the special case of a given class, i.e. predicate
\rdfterm{rdf:type} or $P = a$ and $O = c$, we can use
\rdfterm{void:classPartition} (also defined in section~4.5 in
\cite{voidnote}):
\begin{equation}\label{eq:selSvPaOc}
 \sel{S = ? | P = a \cap O = c } =
    \frac{\rdfterm{void:classPartition/void:triples}}{|d|} .
\end{equation}

@@

This case is similar to the above, and we can write 
\begin{equation}\label{eq:selsuunobpb}
\sel{T_{\{s~p~?\}}} = \sel{O = ? | P = p \cap S = s} \cdot 
\sel{S = s | P = p} \cdot
\sel{P = p} . 
\end{equation}
We note that we can't find the first two parts in the VoID
description\todo{2nd part always 1?}, but we also note with interest that the first part shows
that only the marginal distribution of objects is needed to estimate
this part.

>>>>

We also have in the special case of a given class, i.e. predicate
\rdfterm{rdf:type} or $P = a$ and $O = c$, we can use
\rdfterm{void:classPartition} (also defined in section~4.5 in
\cite{voidnote}) to find the selectivity of the triple pattern:
\begin{equation}\label{eq:selSvPaOc}
 \sel{T_{\{?~a~c\}}} =
    \frac{\rdfterm{void:classPartition/void:triples}}{|d|} .
\end{equation}

@@

This case is similar to the above, and we can write 
\begin{equation}\label{eq:selsuunobpb}
\sel{T_{\{s~p~?\}}} = \sel{O = ? | P = p \cap S = s} \cdot 
\sel{S = s | P = p} \cdot
\sel{P = p} . 
\end{equation}
We note that we can't find the first two parts in the VoID
description\todo{2nd part smaller than a fraction of distinctSubjects?}, but we also note with interest that the first part shows
that only the marginal distribution of objects is needed to estimate
this part.
